---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

library(Lab5)
library(sf)
library(httr)
library(rjson)

```

Most of this information is available scattered throughout the R documentation. This appendix brings it all together in one place. 

With the help of this package it is possible to request data from the Thenmap API (\url{https://www.thenmap.net/}). The function request_API() takes two arguments: "dataset", and "date". With this arguments can the user specify the request. 

## simple example
We'll start by creating a simple request. 

### specify argument and call function request_API
Each of the two arguments has multiple options available: \newline
- **dataset**: ch-8, no-7, no-4, dk-7, se-7, se-4, us-4, gl-7, world-2 \newline
- **date**: Needs to be of format YYYY-MM-DD, YYYY-MM, or YYYY \newline
 \newline

We are requesting a dataset of all national borders, of areas which existed at 1st January 2016, in english language. 
```{r}

dataset <- "world-2"
date <- "2016-01-01"

# request_API <- getFromNamespace("request_API", "Lab5")
requested_data <- request_API(dataset,date)

```

