---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# devtools::install_github("BirgitKarlhuber/Lab5")

library(Lab5)
library(sf)
library(ggplot2)
library(httr)
library(rjson)
```

Most of this information is available scattered throughout the R documentation. This appendix brings it all together in one place. 

With the help of this package it is possible to request data from the Thenmap API (\url{https://www.thenmap.net/}). The function request_API() takes multiple arguments: "version", "dataset", "modules", "date" and "language". With this arguments can the user specify the request. For "modules" there are two possible options: "data" and "geo". With the option "geo" the API returns geo-data. This data can be plotted with the help of the plot_sf_data() function. 


## simple "geo" example
We'll start by creating a simple request for a "geographical" dataset. 

### specify argument and call function request_API
Each of the five arguments has multiple options available: \newline
- **version**: v1, v2 \newline
- **dataset**: ch-8, no-7, no-4, dk-7, se-7, se-4, us-4, gl-7, world-2 \newline
- **modules**: data, geo \newline
- **date**: Needs to be of format YYYY-MM-DD, YYYY-MM, or YYYY \newline
- **language**: fi, ... (not each of the languages is available for all of the datasets) \newline

We are requesting a dataset of all national borders, of areas which existed at 1st January 2016, in english language. 
```{r}

version <- "v1"
dataset <- "world-2"
modules <- "geo"
date <- "2016-01-01"
language <- "en"

# request_API <- getFromNamespace("request_API", "Lab5")
requested_data <- request_API(version,dataset,modules,date,language)

```


### plot the data
By using the plot_sf_data() function it is possible to plot the requested data in a geographical plot. 
```{r}

Lab5::plot_sf_data(requested_data)

```



## simple "data" example
Now we'll create a simple request for a "data" dataset. 


### specify argument and call function request_API
We are requesting a dataset of all Swedish municipalities and their areas and names, in 1974, in Sami language. 
```{r}

# version <- "v2" 
# dataset <- "se-7" 
# modules <- "data" 
# date <- "1974" 
# language <- "se"
# 
# Lab5::requested_data <- request_API(version,dataset,modules,date,language)

```


### Visualize the data

```{r}

# Lab5::xx

```


